Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
Some changes that were accidentally reverted.

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good thema for a commented library~\cite{HydraBattles} of formal proofs written for the \textit{Coq} proof assistant~\cite{Coq}.

Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook}. Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\ref{fig:Ex42E0} and \ref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$. The first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}.

>>>>

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good theme for a commented library~\cite{HydraBattles} of formal proofs written for the \textit{Coq} proof assistant~\cite{Coq}.

Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook} (PDF document of over 280 pages). Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\ref{fig:Ex42E0} and \ref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$. The first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}.
